---
title: "public_analysis"
author: "Roan Buma"
date: "2023-07-21"
output: html_document
---

```{r}
knitr::purl("public_analysis.Rmd")
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading packages and data

```{r}
# PACKAGES
library(dplyr)
library(tidyr)
library(haven)
library(ggplot2)
library(janitor)
```

```{r}
# IMPORT DATA
df_voters = read_sav("C:/sensitive_data/PRECEDE/EVES+COVID+endsurvey/EVES NL + COVID + end survey.sav")
```

```{r eval=FALSE}
# INSPECT DATA
colnames(df_voters)
variable_labels = lapply(df_voters, function(x) attr(x, "label"))
```

```{r}
# SELECTING VARIABLES
df_selection = df_voters %>%
  # precede 3
  select(Q31.Leftrightendsurvey, # LR
         Q32.consprogendsurvey, # cP
         byearendsurvey, # byear
         sex_recendsurvey, # sex
         edu_2_recendsurvey, # edu
         Q24.expen.difficultendsurvey, # making ends meet
         Q10.populism_1endsurvey, # populism 
         Q10.populism_2endsurvey, # populism 
         Q10.populism_3endsurvey, # populism 
         Q10.populism_4endsurvey, # populism 
         Q10.populism_5endsurvey, # populism 
         Q10.populism_6endsurvey, # populism 
         Q10.populism_7endsurvey, # populism 
         Q10.populism_8endsurvey, # populism 
         Q10.populism_9endsurvey, # populism 
         Q10.populism_10endsurvey, # populism 
         Q10.populism_11endsurvey, # populism 
         Q10.populism_12endsurvey, # populism 
         Q10.populism_13endsurvey, # populism 
         Q10.populism_14endsurvey, # populism 
         Q10.populism_15endsurvey, # populism 
         Q10.populism_16endsurvey, # populism 
         Q10.populism_17endsurvey, # populism 
         Q7.PTV.NL_1endsurvey, # PTV
         Q7.PTV.NL_2endsurvey, # PTV
         Q7.PTV.NL_13endsurvey, # PTV
         Q7.PTV.NL_4endsurvey, # PTV
         Q7.PTV.NL_5endsurvey, # PTV
         Q7.PTV.NL_6endsurvey, # PTV
         Q7.PTV.NL_7endsurvey, # PTV
         Q7.PTV.NL_8endsurvey, # PTV
         Q7.PTV.NL_9endsurvey, # PTV
         Q7.PTV.NL_10endsurvey, # PTV
         Q7.PTV.NL_11endsurvey, # PTV
         Q7.PTV.NL_12endsurvey, # PTV
         Q7.PTV.NL_13.0endsurvey, # PTV
         Q7.PTV.NL_14endsurvey, # PTV
         Q7.PTV.NL_15endsurvey, # PTV
         Q7.PTV.NL_16endsurvey, # PTV
         Q7.PTV.NL_17endsurvey, # PTV
         vote.recall_recendsurvey, # vote recall
         Q9.vote.int.NLendsurvey, # vote intent
         Q35.picom_1endsurvey, # picom 1
         Q35.picom_2endsurvey, # picom 2
         Q35.picom_3endsurvey, # picom 3
         Q35.picom_4endsurvey, # picom 4
         Q35.picom_5endsurvey, # picom 5
         Q36.core.populism_1endsurvey, # core populism 1
         Q36.core.populism_2endsurvey, # core populism 2
         Q36.core.populism_3endsurvey, # core populism 3
         Q36.core.populism_4endsurvey, # core populism 4
         Q36.core.populism_5endsurvey, # core populism 5
         Q36.core.populism_6endsurvey, # core populism 6
         Q36.core.populism_7endsurvey, # core populism 7
         Q36.core.populism_8endsurvey, # core populism 8
         Q36.core.populism_9endsurvey, # core populism 9
         Q36.core.populism_10endsurvey, # core populism 10
         Q36.core.populism_11endsurvey, # core populism 11
         Q36.core.populism_12endsurvey, # core populism 12
         Q36.core.populism_13endsurvey, # core populism 13
         Q36.core.populism_14endsurvey, # core populism 14
         Q36.core.populism_15endsurvey, # core populism 15
         Q34.trust_2endsurvey,# trust in media
         Q34.trust_4endsurvey,# trust in twitter
         # PRECEDE 2
         Q32_1covidwv2, # media use tv
         Q32_2covidwv2, # media use internet
         Q32_3covidwv2, # media use newspapers
         Q32_4covidwv2, # media use social media
         Q33covidwv2, # hours spent on internet
         # PRECEDE 1
         # Conspiracy_1covid, # covid conspiracy 1
         # Conspiracy_4covid, # covid conspiracy 2
         # Conspiracy_8covid, # covid conspiracy 3
         # Conspiracy_15covid, # covid conspiracy 4
         # conspiracy_covid_2_22covid, # covid conspiracy 5
         # conspiracy_covid_2_23covid, # covid conspiracy 6
         # conspiracy_covid_2_25covid, # covid conspiracy 7
         # weights
         #weight_trimmed_0.995covid,
         weight_trimmed_0.995covidwv2,
         weight_trimmed_0.995endsurvey
         )
```

```{r}
# FILTERING DATA FOR COMPLETE CASES ONLY (PARTICIPATED IN PRECEDE 1, 2 AND 3)
df_selection = df_selection %>%
  # remove cases with missing data for PRECEDE 3 (end survey)
  #filter(!is.na(weight_trimmed_0.995covid)) %>%
  # remove cases with missing data for PRECEDE 2 (covid wv2)
  filter(!is.na(weight_trimmed_0.995covidwv2)) %>%
  # remove cases with missing data for PRECEDE 1 (covid wv1)
  filter(!is.na(weight_trimmed_0.995endsurvey))
```

```{r}
dim(df_selection)
```

1264 participants participated in PRECEDE_2 and PRECEDE_3 in the Netherlands. 

# DATA PREPARATION

## age

```{r}
# recoding age
df_selection$age = as.numeric(2023 - df_selection$byearendsurvey)
```

## edu

```{r}
attr(df_selection$edu_2_recendsurvey, "labels")

table(df_selection$edu_2_recendsurvey)

df_selection = df_selection %>%
  mutate(edu_rec = case_when(edu_2_recendsurvey == 1 ~ 0,
                             edu_2_recendsurvey == 2 ~ 1,
                             TRUE ~ NA))

table(df_selection$edu_rec, useNA = "ifany")
```

## gender

```{r}
# recoding gender (dummy)
table(df_selection$sex_recendsurvey)
df_selection$woman = ifelse(df_selection$sex_recendsurvey == 1, 0, 1)
table(df_selection$woman)
```

## LR

```{r}
# recoding LR
table(df_selection$Q31.Leftrightendsurvey)
df_selection$LR_rec = df_selection$Q31.Leftrightendsurvey - 1
table(df_selection$LR_rec)
```

## CP

```{r}
# recoding CP
table(df_selection$Q32.consprogendsurvey)
df_selection$CP_rec = df_selection$Q32.consprogendsurvey - 1
table(df_selection$CP_rec)
```

## populism index 1 (17 questions)

```{r}
attr(df_selection$Q10.populism_1endsurvey, which = "label")
attr(df_selection$Q10.populism_2endsurvey, which = "label")
attr(df_selection$Q10.populism_3endsurvey, which = "label")
attr(df_selection$Q10.populism_4endsurvey, which = "label")
attr(df_selection$Q10.populism_5endsurvey, which = "label")
attr(df_selection$Q10.populism_6endsurvey, which = "label")
attr(df_selection$Q10.populism_7endsurvey, which = "label")
attr(df_selection$Q10.populism_8endsurvey, which = "label")
attr(df_selection$Q10.populism_9endsurvey, which = "label")
attr(df_selection$Q10.populism_10endsurvey, which = "label")
attr(df_selection$Q10.populism_11endsurvey, which = "label")
attr(df_selection$Q10.populism_12endsurvey, which = "label")
attr(df_selection$Q10.populism_13endsurvey, which = "label")
attr(df_selection$Q10.populism_14endsurvey, which = "label")
attr(df_selection$Q10.populism_15endsurvey, which = "label")
attr(df_selection$Q10.populism_16endsurvey, which = "label")
attr(df_selection$Q10.populism_17endsurvey, which = "label")
```
```{r}
attr(df_selection$Q10.populism_1endsurvey, which = "labels")
```


```{r}
# recoding for 2, 5, 8 and 14 needed
df_selection = df_selection %>%
  mutate(Q10.populism_2endsurvey_rec = case_when(Q10.populism_2endsurvey == 1 ~ 5,
                                                 Q10.populism_2endsurvey == 2 ~ 4,
                                                 Q10.populism_2endsurvey == 3 ~ 3,
                                                 Q10.populism_2endsurvey == 4 ~ 2,
                                                 Q10.populism_2endsurvey == 5 ~ 1,
                                                 TRUE ~ NA)) %>%
  mutate(Q10.populism_5endsurvey_rec = case_when(Q10.populism_5endsurvey == 1 ~ 5,
                                                 Q10.populism_5endsurvey == 2 ~ 4,
                                                 Q10.populism_5endsurvey == 3 ~ 3,
                                                 Q10.populism_5endsurvey == 4 ~ 2,
                                                 Q10.populism_5endsurvey == 5 ~ 1,
                                                 TRUE ~ NA)) %>%
  mutate(Q10.populism_8endsurvey_rec = case_when(Q10.populism_8endsurvey == 1 ~ 5,
                                                 Q10.populism_8endsurvey == 2 ~ 4,
                                                 Q10.populism_8endsurvey == 3 ~ 3,
                                                 Q10.populism_8endsurvey == 4 ~ 2,
                                                 Q10.populism_8endsurvey == 5 ~ 1,
                                                 TRUE ~ NA)) %>%
  mutate(Q10.populism_14endsurvey_rec = case_when(Q10.populism_14endsurvey == 1 ~ 5,
                                                 Q10.populism_14endsurvey == 2 ~ 4,
                                                 Q10.populism_14endsurvey == 3 ~ 3,
                                                 Q10.populism_14endsurvey == 4 ~ 2,
                                                 Q10.populism_14endsurvey == 5 ~ 1,
                                                 TRUE ~ NA))
```


```{r}
# create df for alpha
df_populism = df_selection %>%
  select(Q10.populism_1endsurvey, # populism 
         Q10.populism_2endsurvey_rec, # populism 
         Q10.populism_3endsurvey, # populism 
         Q10.populism_4endsurvey, # populism 
         Q10.populism_5endsurvey_rec, # populism 
         Q10.populism_6endsurvey, # populism 
         Q10.populism_7endsurvey, # populism 
         Q10.populism_8endsurvey_rec, # populism 
         Q10.populism_9endsurvey, # populism 
         Q10.populism_10endsurvey, # populism 
         Q10.populism_11endsurvey, # populism 
         Q10.populism_12endsurvey, # populism 
         Q10.populism_13endsurvey, # populism 
         Q10.populism_14endsurvey_rec, # populism 
         Q10.populism_15endsurvey, # populism 
         Q10.populism_16endsurvey, # populism 
         Q10.populism_17endsurvey) # populism 

populism_alpha = psych::alpha(df_populism)

# total alpha
populism_alpha$total
```
standardized alpha = .76

```{r}
# create scale
df_selection = df_selection %>%
  mutate(populism_scale_1 = (Q10.populism_1endsurvey+ # populism 
         Q10.populism_2endsurvey+ # populism 
         Q10.populism_3endsurvey+ # populism 
         Q10.populism_4endsurvey+ # populism 
         Q10.populism_5endsurvey+ # populism 
         Q10.populism_6endsurvey+ # populism 
         Q10.populism_7endsurvey+ # populism 
         Q10.populism_8endsurvey+ # populism 
         Q10.populism_9endsurvey+ # populism 
         Q10.populism_10endsurvey+ # populism 
         Q10.populism_11endsurvey+ # populism 
         Q10.populism_12endsurvey+ # populism 
         Q10.populism_13endsurvey+ # populism 
         Q10.populism_14endsurvey+ # populism 
         Q10.populism_15endsurvey+ # populism 
         Q10.populism_16endsurvey+ # populism 
         Q10.populism_17endsurvey)/17) # populism 
```

```{r}
mean(df_selection$populism_scale_1, na.rm=T)
sd(df_selection$populism_scale_1, na.rm=T)
```


## populism index 2 (15 questions)

```{r}
attr(df_selection$Q36.core.populism_1endsurvey, which = "label")
attr(df_selection$Q36.core.populism_2endsurvey, which = "label")
attr(df_selection$Q36.core.populism_3endsurvey, which = "label")
attr(df_selection$Q36.core.populism_4endsurvey, which = "label")
attr(df_selection$Q36.core.populism_5endsurvey, which = "label")
attr(df_selection$Q36.core.populism_6endsurvey, which = "label")
attr(df_selection$Q36.core.populism_7endsurvey, which = "label")
attr(df_selection$Q36.core.populism_8endsurvey, which = "label")
attr(df_selection$Q36.core.populism_9endsurvey, which = "label")
attr(df_selection$Q36.core.populism_10endsurvey, which = "label")
attr(df_selection$Q36.core.populism_11endsurvey, which = "label")
attr(df_selection$Q36.core.populism_12endsurvey, which = "label")
attr(df_selection$Q36.core.populism_13endsurvey, which = "label")
attr(df_selection$Q36.core.populism_14endsurvey, which = "label")
attr(df_selection$Q36.core.populism_15endsurvey, which = "label")
```


```{r}
# recode 2, 6, 8, 14
df_selection = df_selection %>%
  mutate(Q36.core.populism_2endsurvey_rec = case_when(Q36.core.populism_2endsurvey == 1 ~ 5,
                                                 Q36.core.populism_2endsurvey == 2 ~ 4,
                                                 Q36.core.populism_2endsurvey == 3 ~ 3,
                                                 Q36.core.populism_2endsurvey == 4 ~ 2,
                                                 Q36.core.populism_2endsurvey == 5 ~ 1,
                                                 TRUE ~ NA)) %>%
  mutate(Q36.core.populism_6endsurvey_rec = case_when(Q36.core.populism_6endsurvey == 1 ~ 5,
                                                 Q36.core.populism_6endsurvey == 2 ~ 4,
                                                 Q36.core.populism_6endsurvey == 3 ~ 3,
                                                 Q36.core.populism_6endsurvey == 4 ~ 2,
                                                 Q36.core.populism_6endsurvey == 5 ~ 1,
                                                 TRUE ~ NA)) %>%
  mutate(Q36.core.populism_8endsurvey_rec = case_when(Q36.core.populism_8endsurvey == 1 ~ 5,
                                                 Q36.core.populism_8endsurvey == 2 ~ 4,
                                                 Q36.core.populism_8endsurvey == 3 ~ 3,
                                                 Q36.core.populism_8endsurvey == 4 ~ 2,
                                                 Q36.core.populism_8endsurvey == 5 ~ 1,
                                                 TRUE ~ NA)) %>%
  mutate(Q36.core.populism_14endsurvey_rec = case_when(Q36.core.populism_14endsurvey == 1 ~ 5,
                                                 Q36.core.populism_14endsurvey == 2 ~ 4,
                                                 Q36.core.populism_14endsurvey == 3 ~ 3,
                                                 Q36.core.populism_14endsurvey == 4 ~ 2,
                                                 Q36.core.populism_14endsurvey == 5 ~ 1,
                                                 TRUE ~ NA))
```


```{r}
df_populism_core = df_selection %>%
  select(Q36.core.populism_1endsurvey,
         Q36.core.populism_2endsurvey_rec,
         Q36.core.populism_3endsurvey,
         Q36.core.populism_4endsurvey,
         Q36.core.populism_5endsurvey,
         Q36.core.populism_6endsurvey_rec,
         Q36.core.populism_7endsurvey,
         Q36.core.populism_8endsurvey_rec,
         Q36.core.populism_9endsurvey,
         Q36.core.populism_10endsurvey,
         Q36.core.populism_12endsurvey,
         Q36.core.populism_13endsurvey,
         Q36.core.populism_14endsurvey_rec,
         Q36.core.populism_15endsurvey
         )

populism_core_alpha = psych::alpha(df_populism_core)

populism_core_alpha$total
```
standardized alpha = .83

```{r}
# create scale
df_selection = df_selection %>%
  mutate(populism_scale_2 = (Q36.core.populism_1endsurvey+
         Q36.core.populism_2endsurvey_rec+
         Q36.core.populism_3endsurvey+
         Q36.core.populism_4endsurvey+
         Q36.core.populism_5endsurvey+
         Q36.core.populism_6endsurvey_rec+
         Q36.core.populism_7endsurvey+
         Q36.core.populism_8endsurvey_rec+
         Q36.core.populism_9endsurvey+
         Q36.core.populism_10endsurvey+
         Q36.core.populism_12endsurvey+
         Q36.core.populism_13endsurvey+
         Q36.core.populism_14endsurvey_rec+
         Q36.core.populism_15endsurvey)/15)
```


## PTVs

Voters are considered "populist" if they have one of the populist parties in their choice set. This was determined on the basis of Propensity to Vote for those parties (PTV). Respondents answer the question "how likely is it that you will ever vote for the following party:" for each political party in the Netherlands.

In the context of this study, voters that give a 7 or higher to any of the populist parties (PVV, FVD, JA21, BBB) are considered potential populist voters.

PTVs are a better measure than asking people what they will vote if there would be elections today or what they voted in the previous election, because there are so many political parties in the Netherlands and because 

```{r}
table(df_selection$Q7.PTV.NL_1endsurvey)
```

```{r}
# all
attr(df_selection$Q7.PTV.NL_1endsurvey, which = "label")

attr(df_selection$Q7.PTV.NL_2endsurvey, which = "label")

attr(df_selection$Q7.PTV.NL_13endsurvey, which = "label")
df_selection$PTV_SP = as.numeric(df_selection$Q7.PTV.NL_13endsurvey)

attr(df_selection$Q7.PTV.NL_4endsurvey, which = "label")

attr(df_selection$Q7.PTV.NL_5endsurvey, which = "label")
df_selection$PTV_PVV = as.numeric(df_selection$Q7.PTV.NL_5endsurvey)

attr(df_selection$Q7.PTV.NL_6endsurvey, which = "label")

attr(df_selection$Q7.PTV.NL_7endsurvey, which = "label")

attr(df_selection$Q7.PTV.NL_8endsurvey, which = "label")

attr(df_selection$Q7.PTV.NL_9endsurvey, which = "label")

attr(df_selection$Q7.PTV.NL_10endsurvey, which = "label")

attr(df_selection$Q7.PTV.NL_11endsurvey, which = "label")

attr(df_selection$Q7.PTV.NL_12endsurvey, which = "label")

attr(df_selection$Q7.PTV.NL_13.0endsurvey, which = "label")
df_selection$PTV_FVD = as.numeric(df_selection$Q7.PTV.NL_13.0endsurvey)

attr(df_selection$Q7.PTV.NL_14endsurvey, which = "label")
df_selection$PTV_BBB = as.numeric(df_selection$Q7.PTV.NL_14endsurvey)

attr(df_selection$Q7.PTV.NL_15endsurvey, which = "label")
df_selection$PTV_JA21 = as.numeric(df_selection$Q7.PTV.NL_15endsurvey)

attr(df_selection$Q7.PTV.NL_16endsurvey, which = "label")

attr(df_selection$Q7.PTV.NL_17endsurvey, which = "label")
```

```{r}
# populists
attr(df_selection$Q7.PTV.NL_5endsurvey, which = "label")
attr(df_selection$Q7.PTV.NL_13.0endsurvey, which = "label")
attr(df_selection$Q7.PTV.NL_14endsurvey, which = "label")
attr(df_selection$Q7.PTV.NL_15endsurvey, which = "label")
```
```{r}
# create dummy, only 7 or higher (7 because PTV is 1-11 coded)
df_selection$populist_in_choiceset = case_when(
  # populist
  df_selection$Q7.PTV.NL_5endsurvey > 7 ~ 1,
  df_selection$Q7.PTV.NL_13.0endsurvey > 7 ~ 1,
  df_selection$Q7.PTV.NL_14endsurvey > 7 ~ 1,
  df_selection$Q7.PTV.NL_15endsurvey > 7 ~ 1,
  # non populism
  df_selection$Q7.PTV.NL_5endsurvey <= 7 ~ 0,
  df_selection$Q7.PTV.NL_13.0endsurvey <= 7 ~ 0,
  df_selection$Q7.PTV.NL_14endsurvey <= 7 ~ 0,
  df_selection$Q7.PTV.NL_15endsurvey <= 7 ~ 0,
  # NA
  TRUE ~ NA
)

table(df_selection$populist_in_choiceset, useNA = "ifany")
```

## Vote Recall


```{r}
table(df_selection$vote.recall_recendsurvey)

attr(df_selection$vote.recall_recendsurvey, which = "labels")

# need recode
df_selection = df_selection %>%
  mutate(vote.recall_recendsurvey = haven::as_factor(vote.recall_recendsurvey))
```
```{r}
table(df_selection$Q9.vote.int.NLendsurvey)

# recode
df_selection = df_selection %>%
  mutate(Q9.vote.int.NLendsurvey = haven::as_factor(Q9.vote.int.NLendsurvey))

table(df_selection$Q9.vote.int.NLendsurvey)
```

## picom (conspiracy)

```{r}
attr(df_selection$Q35.picom_1endsurvey, which = "label")
attr(df_selection$Q35.picom_1endsurvey, which = "labels")
```


```{r}
# picom
table(df_selection$Q35.picom_1endsurvey)
table(df_selection$Q35.picom_2endsurvey)
table(df_selection$Q35.picom_3endsurvey)
table(df_selection$Q35.picom_4endsurvey)
table(df_selection$Q35.picom_5endsurvey)
```
```{r}
df_selection$picom_1_rec = df_selection$Q35.picom_1endsurvey - 1
df_selection$picom_2_rec = df_selection$Q35.picom_2endsurvey - 1
df_selection$picom_3_rec = df_selection$Q35.picom_3endsurvey - 1
df_selection$picom_4_rec = df_selection$Q35.picom_4endsurvey - 1
df_selection$picom_5_rec = df_selection$Q35.picom_5endsurvey - 1
```

```{r}
# create subdata for picom
df_picom = df_selection %>%
  select(picom_1_rec, picom_2_rec, picom_3_rec, picom_4_rec, picom_5_rec)

# calculate alpha
picom_alpha = psych::alpha(df_picom)

# alpha
picom_alpha$total
```
The PICOM has a high std alpha of .90

```{r}
df_selection = df_selection %>%
  mutate(picom_index = (picom_1_rec + picom_2_rec + picom_3_rec + picom_4_rec + picom_5_rec) / 5)
```
```{r}
table(df_selection$picom_index, useNA = "ifany")
```
## populist vote

```{r}
table(df_selection$vote.recall_recendsurvey)
```


```{r}
df_selection = df_selection %>%
  mutate(populist_vote = case_when(vote.recall_recendsurvey == "PVV" ~ 1,
                                   vote.recall_recendsurvey == "FvD" ~ 1,
                                   vote.recall_recendsurvey == "JA21" ~ 1,
                                   vote.recall_recendsurvey == "BBB" ~ 1,
                                   Q9.vote.int.NLendsurvey == "PVV" ~ 1,
                                   Q9.vote.int.NLendsurvey == "PVV" ~ 1,
                                   Q9.vote.int.NLendsurvey == "PVV" ~ 1,
                                   Q9.vote.int.NLendsurvey == "PVV" ~ 1,
                                   is.na(vote.recall_recendsurvey) ~ NA,
                                   is.na(Q9.vote.int.NLendsurvey) ~ NA,
                                   TRUE ~ 0))

table(df_selection$populist_vote, useNA = "ifany")
```

## coping with income

```{r}
attr(df_selection$Q24.expen.difficultendsurvey, which = "label")

attr(df_selection$Q24.expen.difficultendsurvey, which = "labels")

# rename
df_selection$coping_income = as.numeric(df_selection$Q24.expen.difficultendsurvey)
```

## trust in media

```{r}
attr(df_selection$Q34.trust_2endsurvey, "label")
attr(df_selection$Q34.trust_2endsurvey, "labels")

df_selection$trust_media = as.numeric(df_selection$Q34.trust_2endsurvey)

table(df_selection$trust_media)
```
## trust in Twitter

```{r}
attr(df_selection$Q34.trust_4endsurvey, "label")
attr(df_selection$Q34.trust_4endsurvey, "labels")

df_selection$trust_twitter = as.numeric(df_selection$Q34.trust_4endsurvey)

table(df_selection$trust_twitter)
```
## media use

```{r}
attr(df_selection$Q32_1covidwv2, "label")
attr(df_selection$Q32_1covidwv2, "labels")

df_selection$follow_news_tv = as.numeric(df_selection$Q32_1covidwv2)

table(df_selection$follow_news_tv)
```
```{r}
attr(df_selection$Q32_2covidwv2, "label")
attr(df_selection$Q32_2covidwv2, "labels")

df_selection$follow_news_internet = as.numeric(df_selection$Q32_2covidwv2)

table(df_selection$follow_news_internet)
```
```{r}
attr(df_selection$Q32_3covidwv2, "label")
attr(df_selection$Q32_3covidwv2, "labels")

df_selection$follow_news_newspapers = as.numeric(df_selection$Q32_3covidwv2)

table(df_selection$follow_news_newspapers)
```
```{r}
attr(df_selection$Q32_4covidwv2, "label")
attr(df_selection$Q32_4covidwv2, "labels")

df_selection$follow_news_socialmedia = as.numeric(df_selection$Q32_4covidwv2)

table(df_selection$follow_news_socialmedia)
```

```{r}
# weights
df_selection$weight_trimmed_0.995endsurvey = as.numeric(df_selection$weight_trimmed_0.995endsurvey)
```


```{r}
# create trust differential variable
df_selection$trust_differential = df_selection$trust_media - df_selection$trust_twitter
```


# Analyses

Making dataset smaller

```{r}
# making dataset smaller for analyses
df_analyses = df_selection %>%
  select(age, edu_rec, woman, coping_income, # structural model
         follow_news_tv, follow_news_internet, follow_news_newspapers, follow_news_socialmedia, # media model
         picom_index, #psychological model
         LR_rec, CP_rec, populism_scale_1, # political model
         trust_media, trust_twitter, # dependent variables
         weight_trimmed_0.995endsurvey, # weights
  ) %>%
  # removing cases with missing data
  na.omit()

nrow(df_analyses)
nrow(df_selection)

# how many cases with missing data were removed?
nrow(df_selection) - nrow(df_analyses)
```



## Descriptive Statistics

```{r}
# age
mean(df_analyses$age, na.rm=T)
sd(df_analyses$age, na.rm=T)
min(df_analyses$age)
max(df_analyses$age)
nrow(df_analyses[!is.na(df_analyses$age),])

#hist(df_analyses$age)
```


```{r}
# edu
tabyl(df_analyses$edu_rec)
nrow(df_analyses[!is.na(df_analyses$edu_rec),])
```


```{r}
# gender
tabyl(df_analyses$woman)
nrow(df_analyses[!is.na(df_analyses$woman),])
```

```{r}
# LR
mean(df_analyses$LR_rec, na.rm=T)
sd(df_analyses$LR_rec, na.rm=T)
min(df_analyses$LR_rec, na.rm = T)
max(df_analyses$LR_rec, na.rm = T)
nrow(df_analyses[!is.na(df_analyses$LR_rec),])
```
```{r}
# LR
mean(df_analyses$CP_rec, na.rm=T)
sd(df_analyses$CP_rec, na.rm=T)
min(df_analyses$CP_rec, na.rm = T)
max(df_analyses$CP_rec, na.rm = T)
nrow(df_analyses[!is.na(df_analyses$CP_rec),])
```
```{r}
# news tv
mean(df_analyses$follow_news_tv, na.rm=T)
sd(df_analyses$follow_news_tv, na.rm=T)
min(df_analyses$follow_news_tv, na.rm = T)
max(df_analyses$follow_news_tv, na.rm = T)
nrow(df_analyses[!is.na(df_analyses$follow_news_tv),])
```

```{r}
# news internet
mean(df_analyses$follow_news_internet, na.rm=T)
sd(df_analyses$follow_news_internet, na.rm=T)
min(df_analyses$follow_news_internet, na.rm = T)
max(df_analyses$follow_news_internet, na.rm = T)
nrow(df_analyses[!is.na(df_analyses$follow_news_internet),])
```

```{r}
# news newspapers
mean(df_analyses$follow_news_newspapers, na.rm=T)
sd(df_analyses$follow_news_newspapers, na.rm=T)
min(df_analyses$follow_news_newspapers, na.rm = T)
max(df_analyses$follow_news_newspapers, na.rm = T)
nrow(df_analyses[!is.na(df_analyses$follow_news_newspapers),])
```

```{r}
# news social media
mean(df_analyses$follow_news_socialmedia, na.rm=T)
sd(df_analyses$follow_news_socialmedia, na.rm=T)
min(df_analyses$follow_news_socialmedia, na.rm = T)
max(df_analyses$follow_news_socialmedia, na.rm = T)
nrow(df_analyses[!is.na(df_analyses$follow_news_socialmedia),])
```

```{r}
# trust in media
mean(df_analyses$trust_media, na.rm=T)
sd(df_analyses$trust_media, na.rm=T)
min(df_analyses$trust_media, na.rm = T)
max(df_analyses$trust_media, na.rm = T)
nrow(df_analyses[!is.na(df_analyses$trust_media),])
```

```{r}
# trust in Twitter
mean(df_analyses$trust_twitter, na.rm=T)
sd(df_analyses$trust_twitter, na.rm=T)
min(df_analyses$trust_twitter, na.rm = T)
max(df_analyses$trust_twitter, na.rm = T)
nrow(df_analyses[!is.na(df_analyses$trust_twitter),])
```

```{r}
# populism
mean(df_analyses$populism_scale_1, na.rm=T)
sd(df_analyses$populism_scale_1, na.rm=T)
min(df_analyses$populism_scale_1, na.rm = T)
max(df_analyses$populism_scale_1, na.rm = T)
nrow(df_analyses[!is.na(df_analyses$populism_scale_1),])
```



# Models

## Trust in Media

```{r}
# trust in media model 1
model_trust_media_1 = lm(trust_media ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income),
                       data = df_analyses,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_media_1)
```

```{r}
# trust in media model 2
model_trust_media_2 = lm(trust_media ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income) +
                         # media model
                         scale(follow_news_tv) + scale(follow_news_newspapers) + scale(follow_news_internet) + scale(follow_news_socialmedia),
                       data = df_analyses,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_media_2)
```

```{r}
# trust in media model 3
model_trust_media_3 = lm(trust_media ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income) +# add coping with income
                         # media model
                         scale(follow_news_tv) + scale(follow_news_newspapers) + scale(follow_news_internet) + scale(follow_news_socialmedia) +
                         # psychological model
                         scale(picom_index),
                       data = df_analyses,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_media_3)
```

```{r}
# trust in media model 4
model_trust_media_4 = lm(trust_media ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income) +# add coping with income
                         # media model
                         scale(follow_news_tv) + scale(follow_news_newspapers) + scale(follow_news_internet) + scale(follow_news_socialmedia) +
                         # psychological model
                         scale(picom_index) +
                         # political model
                         scale(LR_rec) + scale(CP_rec) + scale(populism_scale_1),
                       data = df_analyses,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_media_4)
```

```{r}
# comparing models
anova(model_trust_media_1, model_trust_media_2, model_trust_media_3, model_trust_media_4)
```

## Trust in Twitter

```{r}
# trust in twitter model
model_trust_twitter_1 = lm(trust_twitter ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income),
                       data = df_analyses,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_twitter_1)
```

```{r}
# trust in twitter model
model_trust_twitter_2 = lm(trust_twitter ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income) +
                         # media model
                         scale(follow_news_tv) + scale(follow_news_newspapers) + scale(follow_news_internet) + scale(follow_news_socialmedia),
                       data = df_analyses,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_twitter_2)
```

```{r}
# trust in twitter model
model_trust_twitter_3 = lm(trust_twitter ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income) +# add coping with income
                         # media model
                         scale(follow_news_tv) + scale(follow_news_newspapers) + scale(follow_news_internet) + scale(follow_news_socialmedia) +
                         # psychological model
                         scale(picom_index),
                       data = df_analyses,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_twitter_3)
```

```{r}
# trust in twitter model
model_trust_twitter_4 = lm(trust_twitter ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income) +# add coping with income
                         # media model
                         scale(follow_news_tv) + scale(follow_news_newspapers) + scale(follow_news_internet) + scale(follow_news_socialmedia) +
                         # psychological model
                         scale(picom_index) +
                         # political model
                         scale(LR_rec) + scale(CP_rec) + scale(populism_scale_1),
                       data = df_analyses,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_twitter_4)
```

```{r}
anova(model_trust_twitter_1, model_trust_twitter_2, model_trust_twitter_3, model_trust_twitter_4)
```

# Robustness checks

```{r}
# populist vote
df_selection %>%
  filter(!is.na(populist_vote)) %>%
  group_by(populist_vote) %>%
  summarise(mean_trust_media = weighted.mean(Q34.trust_2endsurvey, na.rm = T, w = weight_trimmed_0.995endsurvey), # trust media
            mean_trust_facebook = weighted.mean(Q34.trust_3endsurvey, na.rm = T, w = weight_trimmed_0.995endsurvey), # trust facebook
            mean_trust_twitter = weighted.mean(Q34.trust_4endsurvey, na.rm = T, w = weight_trimmed_0.995endsurvey), # trust twitter
            mean_tv = weighted.mean(Q32_1covidwv2, na.rm = T, w = weight_trimmed_0.995endsurvey), # tv
            mean_newspaper = weighted.mean(Q32_2covidwv2, na.rm = T, w = weight_trimmed_0.995endsurvey), # newspaper
            mean_internet = weighted.mean(Q32_3covidwv2, na.rm = T, w = weight_trimmed_0.995endsurvey), # internet
            mean_socialmedia = weighted.mean(Q32_4covidwv2, na.rm = T, w = weight_trimmed_0.995endsurvey) # social media
            )
```

```{r}
# populist choice set
df_selection %>%
  filter(!is.na(populist_in_choiceset)) %>%
  group_by(populist_in_choiceset) %>%
  summarise(mean_trust_media = weighted.mean(Q34.trust_2endsurvey, na.rm = T, w = weight_trimmed_0.995endsurvey), # trust media
            mean_trust_facebook = weighted.mean(Q34.trust_3endsurvey, na.rm = T, w = weight_trimmed_0.995endsurvey), # trust facebook
            mean_trust_twitter = weighted.mean(Q34.trust_4endsurvey, na.rm = T, w = weight_trimmed_0.995endsurvey), # trust twitter
            mean_tv = weighted.mean(Q32_1covidwv2, na.rm = T, w = weight_trimmed_0.995endsurvey), # tv
            mean_internet = weighted.mean(Q32_2covidwv2, na.rm = T, w = weight_trimmed_0.995endsurvey), # newspaper
            mean_newspaper = weighted.mean(Q32_3covidwv2, na.rm = T, w = weight_trimmed_0.995endsurvey), # internet
            mean_socialmedia = weighted.mean(Q32_4covidwv2, na.rm = T, w = weight_trimmed_0.995endsurvey) # social media
            )
```

Among those with a populist party in their choiceset:
 - trust in media is LOWER
 - trust in facebook is HIGHER
 - trust in twitter is HIGHER
 - tv use same
 - newspaper use lower
 - internet use lower
 - social media use higher

# Tables for Paper

## descriptives

```{r}
library(stargazer)
```

```{r}
continuous_variables = df_analyses[c("age",
                                      "coping_income",
                                      "follow_news_tv",
                                      "follow_news_internet",
                                      "follow_news_newspapers",
                                      "follow_news_socialmedia",
                                      "picom_index",
                                      "LR_rec",
                                      "CP_rec",
                                      "populism_scale_1",
                                      "trust_media",
                                      "trust_twitter")] %>%
  as.data.frame()


stargazer(continuous_variables, digits=2)
```
## regression

```{r}
stargazer(model_trust_twitter_1,
          model_trust_twitter_2,
          model_trust_twitter_3,
          digits = 2
          # covariate.labels = c("Age",
          #                      "Education",
          #                      "Gender",
          #                      "Coping with Income",
          #                      "Follow news TV",
          #                      "Follow news newspapers",
          #                      "Follow news internet",
          #                      "Follow news social media",
          #                      "Conspiracy Beliefs",
          #                      "Left-right",
          #                      "Conservative-Progressive",
          #                      "Populist attitudes",
          #                      "a")
          )
```

```{r}
stargazer(model_trust_twitter_4)
```


```{r}
# shorter model names for stargazer
mtt_1 = model_trust_twitter_1
mtt_2 = model_trust_twitter_2
mtt_3 = model_trust_twitter_3
mtt_4 = model_trust_twitter_4

mtm_1 = model_trust_media_1
mtm_2 = model_trust_media_2
mtm_3 = model_trust_media_3
mtm_4 = model_trust_media_4
```


```{r}
# check model media
# stargazer(mtm_1,
#           mtm_2,
#           mtm_3,
#           mtm_4)

# make beautiful
stargazer(mtm_1,
          mtm_2,
          mtm_3,
          mtm_4,
          digits = 2,
          covariate.labels = c("Age",
                               "Theoretical Education (dummy)",
                               "Woman (dummy)",
                               "Coping with Income",
                               "Follow news TV",
                               "Follow news newspapers",
                               "Follow news internet",
                               "Follow news social media",
                               "Conspiracy Beliefs",
                               "Left-Right",
                               "Conservative-Progressive",
                               "Populist Attitudes",
                               "Constant"),
          # sig cutoff
          star.cutoffs = c(0.05, 0.01, 0.001)
          )
```

```{r}
# check model twitter
stargazer(mtt_1,
          mtt_2,
          mtt_3,
          mtt_4)

# make beautiful
stargazer(mtt_1,
          mtt_2,
          mtt_3,
          mtt_4,
          digits = 2,
          covariate.labels = c("Age",
                               "Theoretical Education",
                               "Woman",
                               "Coping with Income",
                               "Follow news TV",
                               "Follow news newspapers",
                               "Follow news internet",
                               "Follow news social media",
                               "Conspiracy Beliefs",
                               "Left-Right",
                               "Conservative-Progressive",
                               "Populist Attitudes",
                               "Constant"),
          # sig cutoff
          star.cutoffs = c(0.05, 0.01, 0.001)
          )
```

# Robustness Checks (PTV + Trust Differential)

```{r}
# making dataset smaller for analyses
df_analyses_2 = df_selection %>%
  select(age, edu_rec, woman, coping_income, # structural model
         follow_news_tv, follow_news_internet, follow_news_newspapers, follow_news_socialmedia, # media model
         picom_index, #psychological model
         LR_rec, CP_rec, populism_scale_1, # political model
         trust_media, trust_twitter, trust_differential, # dependent variables
         weight_trimmed_0.995endsurvey, # weights
         # populist parties PTVS
         # PTV_SP, # SP
         # PTV_PVV, # PVV
         # PTV_FVD, # FVD
         # PTV_BBB, # BBB
         # PTV_JA21, # JA21
  ) %>%
  # removing cases with missing data
  na.omit()

nrow(df_analyses_2)
nrow(df_selection)

# how many cases with missing data were removed?
nrow(df_selection) - nrow(df_analyses)
```

```{r}
mean(df_analyses_2$trust_differential)
sd(df_analyses_2$trust_differential)
```
```{r}
hist(df_analyses_2$trust_differential)
```

```{r}
table(df_analyses_2$trust_differential)
```

## Model with trust differential

```{r}
# trust in media model 1
model_trust_differential_1 = lm(trust_differential ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income),
                       data = df_analyses_2,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_differential_1)
```

```{r}
# trust in media model 2
model_trust_differential_2 = lm(trust_differential ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income) +
                         # media model
                         scale(follow_news_tv) + scale(follow_news_newspapers) + scale(follow_news_internet) + scale(follow_news_socialmedia),
                       data = df_analyses_2,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_differential_2)
```

```{r}
# trust in media model 3
model_trust_differential_3 = lm(trust_differential ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income) +# add coping with income
                         # media model
                         scale(follow_news_tv) + scale(follow_news_newspapers) + scale(follow_news_internet) + scale(follow_news_socialmedia) +
                         # psychological model
                         scale(picom_index),
                       data = df_analyses_2,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_differential_3)
```

```{r}
# trust in media model 4
model_trust_differential_4 = lm(trust_differential ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income) +# add coping with income
                         # media model
                         scale(follow_news_tv) + scale(follow_news_newspapers) + scale(follow_news_internet) + scale(follow_news_socialmedia) +
                         # psychological model
                         scale(picom_index) +
                         # political model
                         scale(LR_rec) + scale(CP_rec) + scale(populism_scale_1),
                       data = df_analyses_2,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_differential_4)
```

```{r}
# comparing models
anova(model_trust_differential_1, model_trust_differential_2, model_trust_differential_3, model_trust_differential_4)
```

## trust differential table for paper

```{r}
# shorter model names for stargazer
mtd_1 = model_trust_differential_1
mtd_2 = model_trust_differential_2
mtd_3 = model_trust_differential_3
mtd_4 = model_trust_differential_4
```

```{r}
# check model media
stargazer(mtd_1,
          mtd_2,
          mtd_3,
          mtd_4)

# make beautiful
stargazer(mtd_1,
          mtd_2,
          mtd_3,
          mtd_4,
          digits = 2,
          covariate.labels = c("Age",
                               "Theoretical Education (dummy)",
                               "Woman (dummy)",
                               "Coping with Income",
                               "Follow news TV",
                               "Follow news newspapers",
                               "Follow news internet",
                               "Follow news social media",
                               "Conspiracy Beliefs",
                               "Left-Right",
                               "Conservative-Progressive",
                               "Populist Attitudes",
                               "Constant"),
          # sig cutoff
          star.cutoffs = c(0.05, 0.01, 0.001)
          )
```

## PTVs instead of populism scale

```{r}
# making dataset smaller for analyses
df_analyses_3 = df_selection %>%
  select(age, edu_rec, woman, coping_income, # structural model
         follow_news_tv, follow_news_internet, follow_news_newspapers, follow_news_socialmedia, # media model
         picom_index, #psychological model
         LR_rec, CP_rec, populism_scale_1, # political model
         trust_media, trust_twitter, trust_differential, # dependent variables
         weight_trimmed_0.995endsurvey, # weights
         # populist parties PTVS
         PTV_SP, # SP
         PTV_PVV, # PVV
         PTV_FVD, # FVD
         PTV_BBB, # BBB
         PTV_JA21, # JA21
  ) %>%
  # removing cases with missing data
  na.omit()

nrow(df_analyses_2)
nrow(df_selection)

# how many cases with missing data were removed?
nrow(df_selection) - nrow(df_analyses)
```

```{r}
df_analyses_3$PTV_SP = df_analyses_3$PTV_SP - 1
df_analyses_3$PTV_PVV = df_analyses_3$PTV_PVV - 1
df_analyses_3$PTV_FVD = df_analyses_3$PTV_FVD - 1
df_analyses_3$PTV_BBB = df_analyses_3$PTV_BBB - 1
df_analyses_3$PTV_JA21 = df_analyses_3$PTV_JA21 - 1
```


```{r}
hist(df_analyses_3$PTV_SP)
hist(df_analyses_3$PTV_PVV)
hist(df_analyses_3$PTV_FVD)
hist(df_analyses_3$PTV_BBB)
hist(df_analyses_3$PTV_JA21)
```


## Trust in Media

```{r}
# trust in media model 1
model_trust_media_1 = lm(trust_media ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income),
                       data = df_analyses_3,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_media_1)
```

```{r}
# trust in media model 2
model_trust_media_2 = lm(trust_media ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income) +
                         # media model
                         scale(follow_news_tv) + scale(follow_news_newspapers) + scale(follow_news_internet) + scale(follow_news_socialmedia),
                       data = df_analyses_3,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_media_2)
```

```{r}
# trust in media model 3
model_trust_media_3 = lm(trust_media ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income) +# add coping with income
                         # media model
                         scale(follow_news_tv) + scale(follow_news_newspapers) + scale(follow_news_internet) + scale(follow_news_socialmedia) +
                         # psychological model
                         scale(picom_index),
                       data = df_analyses_3,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_media_3)
```

```{r}
# trust in media model 4
model_trust_media_4 = lm(trust_media ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income) +# add coping with income
                         # media model
                         scale(follow_news_tv) + scale(follow_news_newspapers) + scale(follow_news_internet) + scale(follow_news_socialmedia) +
                         # psychological model
                         scale(picom_index) +
                         # political model
                         scale(LR_rec) + scale(CP_rec) +
                         scale(PTV_SP) + scale(PTV_PVV) + scale(PTV_FVD) +scale(PTV_BBB) + scale(PTV_JA21),
                       data = df_analyses_3,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_media_4)
```

```{r}
# comparing models
anova(model_trust_media_1, model_trust_media_2, model_trust_media_3, model_trust_media_4)
```

## Trust in Twitter

```{r}
# trust in twitter model
model_trust_twitter_1 = lm(trust_twitter ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income),
                       data = df_analyses_3,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_twitter_1)
```

```{r}
# trust in twitter model
model_trust_twitter_2 = lm(trust_twitter ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income) +
                         # media model
                         scale(follow_news_tv) + scale(follow_news_newspapers) + scale(follow_news_internet) + scale(follow_news_socialmedia),
                       data = df_analyses_3,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_twitter_2)
```

```{r}
# trust in twitter model
model_trust_twitter_3 = lm(trust_twitter ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income) +# add coping with income
                         # media model
                         scale(follow_news_tv) + scale(follow_news_newspapers) + scale(follow_news_internet) + scale(follow_news_socialmedia) +
                         # psychological model
                         scale(picom_index),
                       data = df_analyses_3,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_twitter_3)
```

```{r}
# trust in twitter model
model_trust_twitter_4 = lm(trust_twitter ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income) +# add coping with income
                         # media model
                         scale(follow_news_tv) + scale(follow_news_newspapers) + scale(follow_news_internet) + scale(follow_news_socialmedia) +
                         # psychological model
                         scale(picom_index) +
                         # political model
                         scale(LR_rec) + scale(CP_rec) +
                         scale(PTV_SP) + scale(PTV_PVV) + scale(PTV_FVD) +scale(PTV_BBB) + scale(PTV_JA21),
                       data = df_analyses_3,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_twitter_4)
```

```{r}
anova(model_trust_twitter_1, model_trust_twitter_2, model_trust_twitter_3, model_trust_twitter_4)
```

## Trust differential

```{r}
# trust in media model 1
model_trust_differential_1 = lm(trust_differential ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income),
                       data = df_analyses_3,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_differential_1)
```

```{r}
# trust in media model 2
model_trust_differential_2 = lm(trust_differential ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income) +
                         # media model
                         scale(follow_news_tv) + scale(follow_news_newspapers) + scale(follow_news_internet) + scale(follow_news_socialmedia),
                       data = df_analyses_3,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_differential_2)
```

```{r}
# trust in media model 3
model_trust_differential_3 = lm(trust_differential ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income) +# add coping with income
                         # media model
                         scale(follow_news_tv) + scale(follow_news_newspapers) + scale(follow_news_internet) + scale(follow_news_socialmedia) +
                         # psychological model
                         scale(picom_index),
                       data = df_analyses_3,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_differential_3)
```

```{r}
# trust in media model 4
model_trust_differential_4 = lm(trust_differential ~ 
                         # structural model
                         scale(age) + scale(edu_rec) + scale(woman) + scale(coping_income) +# add coping with income
                         # media model
                         scale(follow_news_tv) + scale(follow_news_newspapers) + scale(follow_news_internet) + scale(follow_news_socialmedia) +
                         # psychological model
                         scale(picom_index) +
                         # political model
                         scale(LR_rec) + scale(CP_rec) +
                         scale(PTV_SP) + scale(PTV_PVV) + scale(PTV_FVD) +scale(PTV_BBB) + scale(PTV_JA21),
                       data = df_analyses_3,
                       weights = weight_trimmed_0.995endsurvey)

summary(model_trust_differential_4)
```

```{r}
# comparing models
anova(model_trust_differential_1, model_trust_differential_2, model_trust_differential_3, model_trust_differential_4)
```